---
title: "Homework 5"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(patchwork)

set.seed(1)
library(rvest)
library(dplyr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%",
  warning = FALSE,
  message = FALSE)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Problem 1 

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 


## Problem 2

The raw data has 52179 observations of 12 variables, containing date, victim's age, gender, race, sex, name, location, and disposition of the case.
```{r, cache=TRUE}
homicide_df =
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, ", ", state)
  )
```
Below is a data frame showing number of total cases and unsolved cases for each city.
```{r}
unsolved_df =
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(total = n(), unsolved = sum(str_count(disposition, c("Closed without arrest", "Open/No arrest"))))

unsolved_df
```

Prop.test for Baltimore
```{r}
baltimore_test =
  prop.test(906, 2827) %>% 
  broom::tidy() 
  
baltimore_test %>% 
  select(estimate, conf.low, conf.high)
```
Writing function for extracting prop.test estimate and CI

```{r}
prop_test <- function(citystate){
  
   data <- unsolved_df %>% 
    filter(city_state == citystate) 
  
    result <- prop.test(data$unsolved, data$total) %>% 
    broom::tidy() %>% 
    select(estimate, conf.low, conf.high)

    result
}
```

Test for each city

```{r}
test_results_df =
  expand_grid(
  citystate = unsolved_df$city_state
) %>% 
  mutate(
    results_df = map(citystate, prop_test)
  ) %>% 
  unnest(results_df)

test_results_df
```

### Visualization for estimate and CI for each city
```{r}
  test_results_df %>% 
  mutate(estimate = as.numeric(estimate)) %>% 
  mutate(citystate = fct_reorder(citystate, desc(estimate))) %>% 
  ggplot(aes(x = citystate, y = estimate)) + geom_point() + geom_errorbar(aes(ymin = conf.low, ymax = conf.high), position = "dodge", width = 0.25) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + labs(x = "City and State",y = "Estimate and CI",title = "Result of Proportion Test Across Cities")
```


## Question 3

Writing function for extracting t test estimate and p value
```{r}
t_test = function(mu) {
  
  sim_data = tibble(
    x = rnorm(mean = mu, n = 30, sd = 5)
  )
  
  sim_result =
    t.test(sim_data) %>% 
    broom::tidy() %>% 
    select(estimate, p.value) 
}
```

for μ=0
```{r}
mean0_df =
  expand_grid(
  mean = 0,
  iteration = 1:5000
) %>% 
  mutate(
    test_df = map(mean, t_test)
  ) %>% 
  unnest(test_df)
```

for μ=1:6
```{r}
multimean_df =
  expand_grid(
  mean = c(1:6),
  iteration = 1:5000
) %>% 
  mutate(
    test_df = map(mean, t_test)
  ) %>% 
  unnest(test_df)
```

### Plot showing power of t.test and true value of mean

When we increase the mean and keep sigma set to 5, the effect size (μ-0)/5 increase. As effect size increases, power of t.test also increases, keeping null hypothesis the same.
```{r}
multimean_df %>% 
  mutate(
    reject = ifelse(p.value < 0.05, 1, 0)
  ) %>% 
  group_by(mean) %>% 
  summarise(count = n(), reject_count = sum(reject), reject_proportion = reject_count/count) %>%
  ggplot(aes(x = mean, y = reject_proportion)) + geom_point() + geom_line() + labs(x = "True Mean",y = "Power of T.test",title = "Power of t.test v.s multiple means") + scale_x_continuous(limits = c(1,6), breaks = seq(1:6))
  
```

### Plot of average estimate mean and true value of mean

As power of test increased, the sample average of μ̂  across tests for which the null is rejected becomes closer to true value of μ.They are approximately equal to the true value of μ.
```{r}
avg_plot1 =
  multimean_df %>% 
  group_by(mean) %>% 
  summarise(avg = mean(estimate)) %>%
  ggplot(aes(x = mean, y = avg)) + geom_point() + geom_line() + labs(x = "True Mean",y = "Average Estimate of Mean",title = "Average Estimate Mean v.s True Mean") + scale_x_continuous(limits = c(1,6), breaks = seq(1:6))

avg_plot2 = 
  multimean_df %>% 
  mutate(
    reject = ifelse(p.value < 0.05, 1, 0)
  )  %>% 
  filter(reject == 1) %>% 
  group_by(mean) %>% 
  summarise(avg = mean(estimate)) %>%
  ggplot(aes(x = mean, y = avg)) + geom_point() + geom_line() + labs(x = "True Mean",y = "Average Estimate of Mean of Rejected",title = "Average Estimate Mean of Rejected v.s True Mean") + scale_x_continuous(limits = c(1,6), breaks = seq(1:6))

avg_plot1 

avg_plot2
```

